SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-12-04 SI.tex
Update pdfs

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2,3]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[2,4]{Lara S. Bort}             %ORCID: ?
\author[5]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[6]{Fernando Favela-Rosales}
\author[7]{Tiago Mendes Ferreira}
\author[8,9]{Patrick F.J. Fuchs}
\author[10]{Rebeca Garcia-Fandino}
\author[11]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[12,13]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[14]{Norbert Ku{\v c}erka}
\author[15]{Patrik Kula}
\author[16]{Milla Kurki}
\author[11]{Alexander Kuzmin}
\author[26]{Anusha Lalitha} %ORCID: 0000-0002-2817-661X
\author[27,28]{Fabio Lolicato}
\author[17,18]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[2,19,20]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[25]{Cedric Mingham}
\author[29]{Luca Monticelli}
\author[1,30]{Ricky Nencini}
\author[19,20]{Alexey M. Nesterenko}
\author[21]{Thomas J. Piggot}
\author[22]{{\'A}ngel Pi{\~n}eiro}
\author[19,20]{Nathalie Reuter}
\author[12]{Suman Samantray} %ORCID: 0000-0003-3361-9582
\author[10,22,23]{Fabi{\'a}n Su{\'a}rez-Lest{\'o}n}
\author[19,20]{Reza Talandashti}
\author[1,24,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[3]{Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[4]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
%\affil[2]{Affiliation, department, city, postcode, country}
\affil[5]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[6]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[7]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[8]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[9]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[10]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[11]{no affiliation}
\affil[12]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, 52428 Jülich, Germany}
\affil[13]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[14]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}
\affil[15]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[16]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[17]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[18]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[19]{Department of Chemistry, University of Bergen, 5020 Bergen, Norway}
\affil[20]{Computational Biology Unit, Department of Informatics, University of Bergen, 5020 Bergen, Norway}
\affil[21]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[22]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[23]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[24]{VTT Technical Research Centre of Finland, Espoo, Finland}
\affil[25]{Hochschule Mannheim, University of Applied Sciences, Mannheim, Germany}
\affil[26]{Institut Charles Gerhardt Montpellier (UMR CNRS 5253), Universit{\'e} Montpellier, Place Eug{\`e}ne Bataillon, 34095 Montpellier, Cedex 05, France}
\affil[27]{Heidelberg University Biochemistry Center, 69120 Heidelberg, Germany}
\affil[28]{Department of Physics, University of Helsinki, FI-00014 Helsinki, Finland}
\affil[29]{IBCP CNRS, UMR 5086 7, Lyon, France}
\affil[30]{Division of Pharmaceutical Biosciences, Faculty of Pharmacy, University of Helsinki, Helsinki 00014, Finland}

>>>>

\author[1]{Anne M. Kiirikki}         %ORCID: ?
\author[2,3]{Hanne S. Antila}          %ORCID: 0000-0002-2474-5053
\author[2,4]{Lara S. Bort}             %ORCID: ?
\author[5]{Pavel Buslaev}         %ORCID: 0000-0003-2031-4691
\author[6]{Fernando Favela-Rosales}
\author[7]{Tiago Mendes Ferreira}
\author[8,9]{Patrick F.J. Fuchs}
\author[10]{Rebeca Garcia-Fandino}
\author[11]{Ivan Gushchin}
\author[12,13]{Batuhan Kav}           %ORCID: 0000-0003-4990-373X
\author[14]{Norbert Ku{\v c}erka}
\author[15]{Patrik Kula}
\author[16]{Milla Kurki}
\author[11]{Alexander Kuzmin}
\author[26]{Anusha Lalitha} %ORCID: 0000-0002-2817-661X
\author[27,28]{Fabio Lolicato}
\author[17,18]{Jesper J. Madsen}  %ORCID: 0000-0003-1411-9080
\author[2,19,20]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
\author[25]{Cedric Mingham}
\author[29,30]{Luca Monticelli}
\author[1,31]{Ricky Nencini}
\author[19,20]{Alexey M. Nesterenko}
\author[21]{Thomas J. Piggot}
\author[22]{{\'A}ngel Pi{\~n}eiro}
\author[19,20]{Nathalie Reuter}
\author[12]{Suman Samantray} %ORCID: 0000-0003-3361-9582
\author[10,22,23]{Fabi{\'a}n Su{\'a}rez-Lest{\'o}n}
\author[19,20]{Reza Talandashti}
\author[1,24,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Department of Theory and Bio-Systems, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[3]{Department of Biomaterials, Max Planck Institute of Colloids and Interfaces, 14424 Potsdam, Germany}
\affil[4]{University of Potsdam, Institute of Physics and Astronomy, Potsdam-Golm, 14476, Germany}
\affil[5]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, Jyv{\"a}skyl{\"a}, 40014, Finland}
\affil[6]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[7]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[8]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[9]{Universit{\'e} Paris Cit{\'e}, UFR Sciences du Vivant, Paris, 75013, France}
\affil[10]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[11]{no affiliation}
\affil[12]{Institute of Biological Information Processing: Structural Biochemistry (IBI-7), Forschungszentrum Jülich, 52428 Jülich, Germany}
\affil[13]{ariadne.ai GmbH (Germany), Häusserstra{\ss}e 3 Heidelberg 69115, Germany }
\affil[14]{Department of Physical Chemistry of Drugs and Faculty of Pharmacy, Comenius University Bratislava, 832 32 Bratislava, Slovakia}
\affil[15]{Institute of Organic Chemistry and Biochemistry of the Czech Academy of Sciences, Flemingovo n\'{a}m. 542/2,  Prague, CZ-16610, Czech Republic}
\affil[16]{School of Pharmacy, University of Eastern Finland, 70211 Kuopio, Finland}
\affil[17]{Department of Molecular Medicine, Morsani College of Medicine, University of South Florida, Tampa, Florida 33612, United States of America}
\affil[18]{Center for Global Health and Infectious Diseases Research, Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida 33612, United States of America}
\affil[19]{Department of Chemistry, University of Bergen, 5020 Bergen, Norway}
\affil[20]{Computational Biology Unit, Department of Informatics, University of Bergen, 5020 Bergen, Norway}
\affil[21]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}
\affil[22]{Department of Applied Physics, Faculty of Physics, University of Santiago de Compostela, Santiago de Compostela, E-15782, Spain}
\affil[23]{MD.USE Innovations S.L., Edificio Emprendia, 15782 Santiago de Compostela, Spain}
\affil[24]{VTT Technical Research Centre of Finland, Espoo, Finland}
\affil[25]{Hochschule Mannheim, University of Applied Sciences, Mannheim, Germany}
\affil[26]{Institut Charles Gerhardt Montpellier (UMR CNRS 5253), Universit{\'e} Montpellier, Place Eug{\`e}ne Bataillon, 34095 Montpellier, Cedex 05, France}
\affil[27]{Heidelberg University Biochemistry Center, 69120 Heidelberg, Germany}
\affil[28]{Department of Physics, University of Helsinki, FI-00014 Helsinki, Finland}
\affil[29]{University of Lyon, CNRS, Molecular Microbiology and Structural Biochemistry (MMSB, UMR 5086), F-69007, Lyon, France}
\affil[30]{Institut National de la Sant{\'e} et de la Recherche M{\'e}dicale (INSERM), Lyon, France}
\affil[31]{Division of Pharmaceutical Biosciences, Faculty of Pharmacy, University of Helsinki, Helsinki 00014, Finland}
